\documentclass{article}

% Packages
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{enumerate}

% Macros
\newcommand{\ans}[1]{\color{blue} #1 \color{black}}

\begin{document}

    % TITLE SECTION

    \begin{center}
        ************************************ \\
        SEC10 Seminar Talk, Self-Assessment \\
        Edward Speer \\
        \today \\
        ************************************
    \end{center}

    \noindent \emph{Q: What was the FINAL title of your talk?}
    \\ \hfill \\
    Transforming Climate Science: The Secret Sauce of Radiative Transfer
    \\ \hfill \\
    \noindent \emph{Q: If you had to do your Seminar Talk again, what three
                       things would you do differently?}

    \begin{enumerate}[(1)]
    
        \item I feel that while most of my presentation was very clear, my
              explanation of the formula for the TwoStream scheme was a bit hard
              to follow for the audience. The graphics were very clear on the
              slides, but I think I could have done a better job explaining
              exactly how the equation worked.
        \item I would have liked to talk just a bit about the implementation of
              the equations in the CliMA software. I cut any discussion about
              the code implementation for the sake of time, but I think it might
              have been interesting for the audience to see how the equation is
              turned from what seems like should be iteration into matrix based
              operations for speed in my code. Maybe I could have spent a bit
              less time on the theory and more on the implementation, though it
              would be tough for the audience to follow the implementation
              without sufficient discussion of the theory.
        \item I think while I was talking I could have spoken more about the 
              material appearing in the slides. I kept my eyes off the text on
              the slides and spoke at a high level, but there were some points
              on the slides that I could have elaborated on in the theory
              section. For example, I didn't describe what the solar zenith
              angle or leaf angular distributions were, despite the fact that
              they are important parameters of the radiative transfer equation.
              Had I stuck just a bit more to the text on the slides, I wouldn't
              have glossed over them. Whether or not \emph{everything} on the 
              slides needed to be said, planning in advance those parts that I
              needed to make \emph{sure} were said would have been helpful - 
              i.e laying out the key elements of the story I wanted to tell in 
              advance would ensure I didn't skip any of them.

    \end{enumerate}

\end{document}
