There is one other sense in which non-locality remains in the MWI, and we should
consider it to determine whether it threatens the local causality we have been
careful to protect. This non-locality is known as the problem of separability.

Consider again the EPR state. We have two particles with anti-aligned spins,
meaning that the spin of one is always opposite the spin of the other. The
measurement of one particle will always inform us of the state of the other
particle. Regardless of the interpretation of quantum mechanics one chooses, 
there is a sense in which the specification of this state alone represents a 
non-locality. I am presented with two particles in two different locations whose
states cannot be fully specified independently from each other. For example, I
can describe the state of one particle as a reduced density matrix by tracing
over the other particle, but I will fundamentally be losing some of the state
information about the particle when I do so — notably the correlation of its 
spin to the other particle. In the MWI, this akin to Alice knowing which version
of Bob she can meet once she measures her own particle. Note that this is a fact
about the nature of entanglement itself, and so \emph{no} interpretation of
quantum mechanics can escape this sort of non-locality.

However, what sort of threat can this variety of non-locality pose to local 
causality? We have already established that the correlations between the 
particles in the MWI do not represent causal influences, but how should we think
about this intermingling of the state?

The answer is simple — the correlation between the two particles is endowed to
them by the preparation of the state. It's true that the we cannot have a fully
local description of the state of each particle without reference to the other
particle across space, but this is not an issue in our causal picture because
the state was prepared this way in a local setting. The preparation of the state
is a local event, and after the state is prepared, the correlations between the
particles remain fixed in the EPR state. Thus, while this non-locality remains
in the MWI and represents a departure from classical intuition, it does not 
threaten the causality we were seeking to protect.
