\documentclass{article}

% Packages
\usepackage{fullpage}
\usepackage{graphicx}

% Macros
% INSERT DRAFT NUM HERE
\newcommand{\HWNUM}{1}

\begin{document}

    % TITLE SECTION

    \begin{center}
        ************************************ \\
        SEC10 Pitch Draft, Revision \HWNUM \\
        Edward Speer \\
        \today \\
        ************************************
    \end{center}

    The entry barrier to high precision embedded software development is 
    monstrous. The cost of development hardware and tools is high, and the 
    risk of burning a device in the tool-up process is higher. But what if I told
    you there was a way to make this process easier, cheaper, and more accessible
    to developers, students, and hobbyists alike?
    
    High precision embedded applications require specialized hardware that
    supports high resolution timing and runs a real-time operating system. 
    If you want that packages with high computing performance, you're going to 
    pay a premium. The question therefore becomes: how can we make this
    technology more accessible to the masses? \\ \hfill \\

    Cloud computing services have already revolutionized the way we think about
    computing and access high performance compute resources, and remain on 
    the rise. Leveraging the power of cloud computing, we can provide a 
    platform allowing developers to develop, test, and deploy high precision 
    embedded applications without ever needing to purchase expensive hardware. 
    This platform would provide users with a development environment that 
    supports high resolution timing, real-time operating systems natively, 
    allowing them to develop and test their applications, and collect data on 
    the performance of their applications on real hardware.

    With RTOS compute time widely available, developers can focus on the
    development of their applications, and not worry about the cost of
    the development hardware. Similarly to how cloud computing brought about 
    rapid development in the AI and machine learning space, this platform
    will bring about a phase of rapid development and discovery in real-time 
    embedded applications, driving the development of impactful new technologies.

    While acting as a massive boon to developers, this platform will also grant 
    students and hobbyists access to high precision embedded development tools
    that were previously out of reach, ushering in a new era of innovation in
    the embedded system space. Demand for high precision embedded systems is
    on the rise, meaning there is a significant market opportunity for this
    platform.

    Following in the footsteps of other cloud computing services, this platform
    will be offered on a pay-as-you-go basis, allowing users to pay only for the
    resources they use. This will make the platform mutually beneficial,
    empowering developers while turning a significant profit. \\ \hfill \\

    The future of embedded systems development is here, and it's in the cloud. 
    With this new cloud-hosted RTOS compute platform, we will revolutionize the way developers, students,
    and hobbyists think about embedded systems development, and drive the
    emergence of new technologies that will shape the future of the embedded
    systems space.  With your help, we can make this vision a reality and 
    deliver incredible value to developers and the world at large.

\end{document}